---
title: "Special Work Performance 2"
author:  Group 17 - Spencer
  Arney (583252), David Berscheid (580687), \newline Marvin Gauer (580553), Cemre Uenal (585962), 
fontsize: 12pt 
geometry: margin=1in
output:
  word_document:
  pdf_document:
    keep_tex: yes


---

###To do:
1) Create content in RMarkdown file and get a Word output file

2) Do all the formating in the end and in Word
    - not more than 5 pages
    - change font to Times Roman in 12pt with 1.15 line spacing
    - in tables and graphs you may use 10pt and 1.0 line spacing
    - 1 inch space on all sides (Done by RMarkdown)
    - report names, group number, student numbers, page number (Done by RMarkdown)


```{r include = TRUE, echo = FALSE, comment = NA}
knitr::opts_chunk$set(fig.width=4, fig.height=2.8)
```
```{r include = FALSE}
rm(list=ls())

library(ggplot2)
library(car)
library(stringi)
library(psych)
library(dplyr)
library(corrplot)

data(Salaries)
```


###Example Question: Draw a visualization of all bivariate relationships.
```{r include = TRUE, echo = FALSE, comment = NA}
SalariesRel <-  Salaries %>%
  mutate_if(is.factor, as.numeric)

library(corrplot)
# par(mar=c(5,6,4,5)+2)
corrplot(corr = cor(SalariesRel))
```

The visualization shows all bivariate relationships, more precisely respective correlations. The bigger the circle the more extreme the correlation. Results that are worth mentioning are... 



    